\bf On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2024-04-16 manuscript/manuscript.tex
more details to UG teaching section

% Undergraduate level (could mention AZ's undergraduate thesis)

>>>>

% Undergraduate level (could mention AZ's undergraduate thesis)
At the undergraduate level, so far only the misuses of one-sample KS test have 
been presented and demonstrated in a classroom setting. At UConn, ES 
incorporated this material in STAT 3215, Applied Linear Regression in Data 
Science, as the one-sample KS test is used in residual diagnostics for testing 
whether the externally studentized residuals can be viewed as realizations of a 
standard normal distribution for large samples. %The catalog description of this 
%course states the following topics: ``Applied multiple 
%linear regression analysis in data science, with an emphasis on modern 
%statistical regression methods: simple linear regression and correlation 
%analysis, multiple linear regression, analysis of variance, goodness of fit, 
%comparing regression models through partial and sequential F tests, dummy 
%variables, regression assumptions and diagnostics, model selection and penalized 
%regression, prediction and model validation, principles of design of experiments, 
%one-way and two-way analysis of variance.'' 
Students in this applied linear regression course are required
to have taken either two semesters of introductory statistics or a 
Calculus~2-based statistical methods course as a prerequisite. In the KS 
assignment, students were introduced to a more detailed description of the KS 
test, and were provided R code and output for a simulation study that showed  
KS test performance (in terms of the distribution of $p$-values) under a 
scenario where all KS test assumptions were met (independent, continuous data 
with precisely specified hypothesized distributions). When the scenario was 
modified to use estimated parameters instead, the students were asked modify the 
previous simulation code and show the resulting distribution of $p$-values. The 
assignment is included in the Supplemental Materials.

While students in this course are exposed to the bootstrap in the 
context of linear regression models (specifically, case resampling and residual 
bootstrap), they are not in general familiar with serially dependency. Thus, the 
remedies and more complicated serially dependent settings were not presented in 
the undergraduate applied linear regression course. Serial dependence is covered 
in other undergraduate courses, and in fact, the contents of this manuscript 
were the basis of AZ's undergraduate honors thesis. Consequently, all 
statistical concepts and methods employed within this paper are certainly within 
reach of many UConn undergraduate Statistics and Statistical Data Science 
majors.
